An HPSG account for deliminative verbal reduplication in Mandarin Chinese

### 2024-08-18 chapters/ch02-Phenomenon.tex
Update 2024-08-18-22:12:26

\ea\label{ex:forms-mono} for monosyllabic verbs: \obj{shuo1} `say'
	\ea \gll \objex{shuo1-shuo}\\ 
		say-say\\ \jambox{AA}
		\ex \gll \objex{shuo1-yi-shuo1}\\
		say-one-say\\ \jambox{A-\textit{yi}-A}
		\ex \gll \objex{shuo1-le-shuo1}\\
		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
		\ex \gll \objex{shuo1-le-yi-shuo1}\\
		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
		\ex \gll \objex{shuo1-shuo1-kan4}\\
		say-say-look\\ \jambox{AA-\obj{kan4}}
		\ex \gll \objex{shuo1-kan4-kan4}\footnotemark\\
		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}}
		\z
\footnotetext{One reviewer points out that this form is not acceptable for him/her.
The acceptability of the A-\obj{kan4-kan4} form seems to vary among Mandarin Chinese speakers.
\citet[73]{Cheng2012} suggests that unlike AA-\obj{kan4}, A-\obj{kan4-kan4} is an emerging construction that is still undergoing grammaticalization.
He found in the Academia Sinica Balanced Corpus of Modern Chinese (Sinica Corpus; \citealt{sinica}) 23 tokens of A-\obj{kan4-kan4} but 141 tokens of AA-\obj{kan4} (p. 64).
This shows that the former is less common than the latter.
(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
\gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
\glt `Let's just follow the north wind, try and see if we can block the sand!'
\z

@@

\begin{sloppypar}
\ea\label{ex:nonvol}
\ea
\gll keshi xian mujin, dajia ye zhihao \textit{weiqu-weiqu} le.\\
but now current everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
\glt `But now, everybody can only feel wronged a little bit.'

\ex
\gll ta-men neng zuo de buguo shi \textit{ren-ren-xing} shua dian'er xiao piqi \textit{diao-diao} yanlei shenme de.\\
she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \textsc{de}\\ \jambox{({CCL})}
\glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
\z
\z
\end{sloppypar}

It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
Compared to the questionable reduplication of the stative verb \textit{bing} `be sick' in (\ref{ex:redup-stat})
and that of the achievement verb \textit{ying} `win' in (\ref{ex:redup-achiV}), 
the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) is readily acceptable.

@@

\ea
\ea[?]
{\gll ta \textit{bing-bing} jiu hao le.\\
he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
Intended: `He was sick for a little while and then got well.'}\label{ex:redup-stat}

\ex[?]
{\gll ta \textit{ying}-\textit{le}-\textit{ying} na chang bisai.\\
he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
\glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}

\ex[]
{\gll ta \textit{kan}-\textit{le}-\textit{kan} na chang bisai.\\
he watch-\textsc{pfv}-watch that \textsc{clf} competition\\
\glt `He watched that competition for a little while.' \\}\label{ex:redup-actV}

\ex[]
{\gll ta \textit{kesou-kesou} jiu hao le.\\
he cough-cough then well \textsc{ptc}\\
\glt `He coughed a little bit and then got well.'}\label{ex:redup-semel}
\z
\z

However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat3}) were found in novels and plays written by native speakers and example sentences like (\ref{ex:redup-achi-stat4}) and (\ref{ex:redup-achi-stat5}) constructed by native speaker linguists.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' and stative verbs like \textit{shutan} `be comfortable', \textit{lian'ai} `be in love' and \textit{bing} `be sick' are reduplicated.

@@

\footnotetext[2]{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
%\begin{sloppypar}
\ea
\ea\label{ex:redup-achi-stat1}
\gll deng ren-men ba zhe jian shi \textit{wang}-\textit{wang} zai shuo ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\

\ex\label{ex:redup-achi-stat2}
\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
\glt `Let's take a bath later and be comfortable for a little while.'\\

\ex\label{ex:redup-achi-stat3}
\gll \textit{lian}-\textit{lian}-\textit{ai} shi keyi de, ban xishi dinghao chi yidian.\footnotemark\\
like-like-love \textsc{cop} ok \textsc{de} host wedding best late a.bit\\
\glt `It's ok to be in love a little bit, but it's better to get married a bit later.'\\

\ex\label{ex:redup-achi-stat4}
\gll wo zhen xiang \textit{bing-yi-bing}, xie ta ge shi tian ban yue.\\
I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
\glt `I really want to be sick for a little while and rest for ten days or half a month.'

\ex\label{ex:redup-achi-stat5}
\gll jiao ta \textit{sheng-sheng} xiaohai, jiu zhidao zuo muqin de gan-ku le.\\
let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
\z
\z
%\end{sloppypar}

This shows that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
this is by no means a rigid constraint, 
and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.

>>>>

\ea\label{ex:forms-mono} for monosyllabic verbs: \obj{shuo1} `say'
	\ea \gll \objex{shuo1-shuo}\\ 
		say-say\\ \jambox{AA}
		\ex \gll \objex{shuo1-yi-shuo1}\\
		say-one-say\\ \jambox{A-\textit{yi}-A}
		\ex \gll \objex{shuo1-le-shuo1}\\
		say-\textsc{pfv}-say\\ \jambox{A-\textit{le}-A}
		\ex \gll \objex{shuo1-le-yi-shuo1}\\
		say-\textsc{pfv}-one-say\\ \jambox{A-\textit{le}-\textit{yi}-A}
		\ex \gll \objex{shuo1-shuo1-kan4}\\
		say-say-look\\ \jambox{AA-\obj{kan4}}
		\ex \gll \objex{shuo1-kan4-kan4}\\
		 say-look-look\\ \jambox{A-\obj{kan4}-\obj{kan4}\footnotemark}
		\z
\footnotetext{One reviewer points out that this form is not acceptable for him/her.
The acceptability of the A-\obj{kan4-kan4} form seems to vary among Mandarin Chinese speakers.
\citet[73]{Cheng2012} suggests that unlike AA-\obj{kan4}, A-\obj{kan4-kan4} is an emerging construction that is still undergoing grammaticalization.
He found in the Academia Sinica Balanced Corpus of Modern Chinese (Sinica Corpus; \citealt{sinica}) 23 tokens of A-\obj{kan4-kan4} but 141 tokens of AA-\obj{kan4} (p. 64).
This shows that the former is less common than the latter.
(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
\gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
\glt `Let's just follow the north wind, try and see if we can block the sand!'
\z

@@

\begin{sloppypar}
\ea\label{ex:nonvol}
\ea
\gll \objex{ke3shi4} \objex{xian4mu4jin1}, \objex{da4jia1} \objex{ye3} \objex{zhi3hao3} \obj{wei3qu1-wei3qu1} le.\\
but now  everybody also can.only feel.wronged-feel.wronged \textsc{ptc}\\ \jambox{({CCL})}
\glt `But now, everybody can only feel wronged a little bit.'

\ex
\gll \objex{ta1-men} \objex{neng2} \objex{zuo4} de \objex{bu2guo4} \objex{shi4} \obj{ren4-ren4-xing4}, \objex{shua3} \objex{dian3'er} \objex{xiao3} \objex{pi2qi4}, \obj{diao4-diao} \objex{yan3lei4} \objex{shen2mede}.\\
she-\textsc{pl} can do \textsc{de} just be be.willful-be.willful-temperament play a.little small temper drop-drop tear what \\ \jambox{({CCL})}
\glt `What they can do is just to be a little bit willful, to lose their temper a little bit and to drop a little bit of tears or something.'
\z
\z
\end{sloppypar}

It is true that  the reduplication of stative and achievement verbs is not as easily acceptable as that of activities and semelfactives.
\citep[155]{XiaoMcEnery2004} classify \obj{bing4} `be sick' as a stative verb.
Indeed, compared  to the questionable reduplication of \obj{bing4} `be sick' in (\ref{ex:redup-stat}),  
 the reduplication of the activity verb \textit{kan} `watch' in (\ref{ex:redup-actV})
and that of the semelfactive verb \textit{kesou} `cough' in (\ref{ex:redup-semel}) are readily acceptable.

@@

\ea
\ea[?]
{\gll \objex{ta1} \obj{bing4-bing} \objex{jiu4} \objex{hao3} le.\\
he be.sick-be.sick then well \textsc{ptc}\\ \jambox{\citep[155]{XiaoMcEnery2004}}
Intended: `He was sick for a little while and then got well.'}\label{ex:redup-stat}

\ex[]
{\gll \objex{ta1} \obj{kan4}-\obj{le}-\obj{kan4} \objex{na4} \objex{chang3} \objex{bi3sai4}.\\
he watch-\textsc{pfv}-watch that \textsc{clf} competition\\
\glt `He watched that competition for a little while.' \\}\label{ex:redup-actV}

\ex[]
{\gll \objex{ta1} \obj{ke2sou4-ke2sou4} \objex{jiu4} \objex{hao3} le.\\
he cough-cough then well \textsc{ptc}\\
\glt `He coughed a little bit and then got well.'}\label{ex:redup-semel}
\z
\z

However, examples such as (\ref{ex:redup-achi-stat4}) can be found where \obj{bing4} `be sick' is reduplicated.

\ea\label{ex:redup-achi-stat4}
\gll \objex{wo3} \objex{zhen1} \objex{xiang3} \obj{bing4-yi-bing4}, \objex{xie1} \objex{ta1} \objex{ge} \objex{shi2} \objex{tian1} \objex{ban4} \objex{yue4}.\\
I really want be.sick-one-be.sick rest it \textsc{clf} ten day half month\\ \jambox{\citep[54]{Chen2001}}
\glt `I really want to be sick for a little while and rest for ten days or half a month.'
\z

As a reviewer points out, \citet[Sec. 3.3]{Tham2013} considers  \obj{bing4} `be sick' to be a basic change of state (COS) verb, i.e. `become sick'.
In contrast, she uses \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as examples of stative verbs.
\citet[680]{PeckEtAl2013} also list \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as stative verbs.
For these two verbs, examples such as (\ref{ex:xihuan}) and (\ref{ex:xiangxin}) can be found.
\ea\label{ex:xihuan}%这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan4} \objex{bu4xing2} \objex{me}?\\
this car so cool \textsc{ptc} what \textsc{ptc} I just like-like cannot \textsc{ptc}\\\jambox{(BCC)}
\glt `This car is so cool! What? I can't just like it for a little bit?'

\ex\label{ex:xiangxin}%谁让我来相信相信 (CCL)
\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \objex{xiang1xin4-xiang1xin4}\\
who let I come believe-believe\\\jambox{(CCL)}
\glt `Who lets me believe him/her?'
\z

On the other hand, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a COS interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
    Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
    Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
    and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
    these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} Ān\objex{yu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} Ān\objex{yu3} \objex{ni3} \objex{kuai4dian} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
\z
\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}

One might argue that even in the examples above, dynamic rather than stative meaning is conveyed.
We argue that the dynamic interpretation does not come from the verb but from reduplication.
The use of reduplication affects the situation aspect at the sentential level.
And as we describe in \sectref{sec:core-sem}, the semantics of reduplication has the property dynamicity.
Verbs such as \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene' are stative in a neutral context and thus, we consider the intrinsic feature of these verbs to be stative
and they should be classified as stative verbs.
The dynamic interpretation only arises when they are used in specific contexts, in this case, when they are reduplicated.

Similar to stative verbs, the reduplication of achievement verbs is also not readily acceptable,
as shown in (\ref{ex:redup-achiV}) with reduplication of \obj{ying2} `win'.

\ea[?]
{\gll \objex{ta1} \obj{ying2}-\obj{le}-\obj{ying2} \objex{na2} \objex{chang3} \objex{bi3sai4}.\\
    he win-\textsc{pfv}-win that \textsc{clf} competition\\ \jambox{\citep[155]{XiaoMcEnery2004}}
    \glt Intended: `He won that competition a little bit.'}\label{ex:redup-achiV}
\z

However, examples such as those in (\ref{ex:redup-achi-stat1}--\subref{ex:redup-achi-stat5}) can be found.
Here, achievement verbs like \textit{wang} `forget' and \textit{sheng} `give birth to' are reduplicated.

@@

%\footnotetext[3]{Tian, Han. 1959. \textit{Tianhan xuanji [Selected works of Tianhan]}, 122. Beijing: People's Literature Publishing House.}
%\footnotetext[4]{Zhou, Libo. 1958. \textit{Shang xiang ju bian [Big changes of mountains and the countryside]}, 204. Beijing: The Writers Publishing House.}
%\begin{sloppypar}
\ea
\ea\label{ex:redup-achi-stat1}
\gll \objex{deng3} \objex{ren2-men} ba \objex{zhe4} \objex{jian4} \objex{shi4} \obj{wang4}-\obj{wang} \objex{zai4} \objex{shuo1} ba.\footnotemark\\
wait people-\textsc{pl} \textsc{ba} this \textsc{clf} incident forget-forget then talk \textsc{ptc}\\
\glt `Let's wait until people forget this incident a little bit and then talk about it.'\\
\footnotetext{Liu, Zhen. 1963. \textit{Chang chang de liushui [Long long water]}, 72. Beijing: The Writers Publishing House.}
%\ex\label{ex:redup-achi-stat2}
%\gll huitou mo ge zao \textit{shutan}-\textit{shutan} ba.\footnotemark\\
%later wipe \textsc{clf} bath be.comfortable-be.comfortable \textsc{ptc}\\
%\glt `Let's take a bath later and be comfortable for a little while.'\\

%\ex\label{ex:redup-achi-stat3}
%\gll \textit{lian}-\textit{lian}-\textit{ai} shi keyi de, ban xishi dinghao chi yidian.\footnotemark\\
%like-like-love \textsc{cop} ok \textsc{de} host wedding best late a.bit\\
%\glt `It's ok to be in love a little bit, but it's better to get married a bit later.'\\

\ex\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi}\ldots \\
we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
\glt `We women can only give birth to children \ldots'

\ex\label{ex:redup-achi-stat5}
\gll \objex{jiao4} \objex{ta1} \obj{sheng1-sheng1} \objex{xiao3hai2}, \objex{jiu4} \objex{zhi1dao4} \objex{zuo4} \objex{mu3qin1} de \objex{gan1-ku3} le.\\
let she give.birth.to-give.birth.to child then know \textsc{cop} mother \textsc{de} sweet-bitter \textsc{ptc}\\ \jambox{\citep[112]{Chen2005}}
\glt `Let her try to give birth to a child and then she will know the bittersweetness of being a mother.'
\z
\z
%\end{sloppypar}

The reduplication does not seem to cancel the \textit{telos} of achievements.
Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
\ea
\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
    \gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\ldots\\
    together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
    \glt `(We) together \ldots\, went to the market nearby to buy some things.'}

\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
    \gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}.\\
    two day later arrive nearby market buy-buy thing\\
    \glt `Two days later, (we) went to the market nearby to buy some things.}

\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}.\\
    arrive nearby market buy-buy thing two day\\
    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
\z\z
The following continuation that cancels the \textit{telo} is also infelicitous (\ref{ex:telod}).
\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}.\\
arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
\z
These tests suggest that the reduplicated verbs are indeed achievements,
rather than being used as activities.

The examples presented in this section show that although the reduplication does have a tendency to interact with volitional verbs and with activities and semelfactives due to its dynamic meaning, 
this is by no means a rigid constraint, 
and non\hyp{}volitional verbs, states and achievements can be reduplicated in appropriate contexts as well,
 contrary to common beliefs in the literature.
Thus, a theoretical account of reduplication should not restrict its use to only certain verb classes.
